On the surprising effectiveness of a simple matrix exponential derivative approximation, with application to global SARS-CoV-2

### 2023-09-14 manuscript/revision_letter.tex
first paragraph

In particular, we have:
\begin{itemize}
	\item clarified how the present work complements its companion paper \citet{magee2023random}, which presents scaling and simulation studies;

@@

    \item compared scalability of surrogate-trajectory HMC with the naive and affine-corrected approximations;

    \item improved upon the SARS-CoV-2 application, relating it to previously established results;

@@

In short, our original goal was not to prove validity of the general methodology, which we saw as already established through simulation studies, real-world analyses and measure theoretic probability.

@@

@@

>>>>

In particular, we have:
\begin{itemize}
	\item clarified how the present work relates to our other work that includes thorough simulation studies \citet{magee2023random} and provides strong theoretical guarantees for surrogate-trajectory HMC \citet{glatt2020accept};

@@

    \item expanded upon the SARS-CoV-2 application, relating it to previously established results and improving a key figure;

@@

In short, our original goal was not to prove validity of the general methodology, which we saw as already established through simulation studies, real-world analyses and measure theoretic arguments.

@@

\begin{reply}
	Again, we thank you for catching this error and have fixed the numbering accordingly. 
\end{reply}

@@

\begin{reply}
	It is clear that the opening sentence missed its mark.  We have edited the first paragraph to read:
	\begin{quote}
		Phylogeographic methods
	\cite{lemey2009bayesian, lemey2014unifying, holbrook2021massive,
	holbrook2022viral} model large-scale viral transmission between
human populations as a function of the shared evolutionary history of
the viral population of interest.  Data take the form of dates,
locations and genome sequences associated to individual viral
samples. Spatiotemporal structure interfaces with network structure
given by the phylogeny, or family tree, describing the viruses'
collective history beginning with the most recent common ancestor.
While one cannot directly observe this history, one may statistically
reconstruct the phylogenetic tree by positing that changes in the
viral genome happen randomly at regular intervals, thereby capturing
the intuition that viral samples with more differences between their
(aligned) sequences should find themselves further apart on the family
tree.
	\end{quote}
\end{reply}
